```{r setup-Potenzgesetze, include=FALSE}
# ---------------------------------------------------------------------------
#% maintainer:
#%   - Norman Markgraf (nmarkgraf@hotmail.com)
#%
# ---------------------------------------------------------------------------
source("../prelude.R")
initPart(
    "Potenzgesetze",  # Dateiname ohne Suffix
    "Potenzgesetze"        # Verzeichnisname im Bilderverzeichnis 
    )
pathToImages <- getPathToImages()
# ---------------------------------------------------------------------------

library(mosaic)

```


### Potenzgesetze

:::::: {.columns}
::: {.column width="49%"}

**Potenzregeln:**

1. $\displaystyle a^0 \stackrel{\text{def}}{=} 1$\setlength{\itemsep}{12pt}

2. $\displaystyle a^x \cdot a^y = a^{x+y}$

3. $\displaystyle a^x \cdot b^x = (a \cdot b)^x$

4. $\displaystyle\left(a^x\right)^y = a^{x \cdot y}$

5. $\displaystyle a^{-x} = \frac{1}{a^x}$

6. $\displaystyle\frac{a^x}{a^y} = a^{x-y}$

7. $\displaystyle\frac{a^x}{b^x} = \left(\frac{a}{b}\right)^x$

8. $\displaystyle\sqrt[n]{a} \stackrel{\text{def}}{=} a^{\frac{1}{n}}$

:::
::: {.column width="49%"}

**Beispiele:**

1. $\displaystyle 5^0 = 1$\setlength{\itemsep}{12pt}

2. $\displaystyle 2^3 \cdot 2^4 = 2^{3+4} = 2^7$

3. $\displaystyle 3^5 \cdot 4^5 = (3 \cdot 4)^5$

4. $\displaystyle\left(2^3\right)^4 = 2^{3\cdot 4} = 2^{12}$

5. $\displaystyle 2^{-3} = \frac{1}{2^3}$

6. $\displaystyle\frac{6^4}{6^2} = 6^{4-2}=6^2$

7. $\displaystyle\frac{10^5}{5^5} = \left(\frac{10}{5}\right)^5=2^5$

8. $\displaystyle\sqrt[5]{32} = 32^{\frac{1}{5}} =32^{0{,}2} = 2$

:::
::::::


### Übungsaufgaben

:::::: {.columns}
::: {.column width="49%"}

a) $\displaystyle\frac{\left(2^2\right)^3 \cdot \left(2^2\right)^4}{2^{14}}=$\setlength{\itemsep}{12pt}

b) $\displaystyle\frac{5^7\cdot \left(2 \cdot 5\right)^3\cdot 2^7}{\left(2 \cdot 2 \cdot 5\right)^7}=$ 

c) $\displaystyle\frac{\left(2^2\cdot3\right)^2\cdot7^4\cdot\left(2\cdot3\right)^2}{2 \cdot(7 \cdot 3 \cdot 2)^{4}}=$

d) $\displaystyle 4 \cdot a^{(m+1)n} \cdot a^{m-n} \cdot\left(a^{mn+m}\right)^{-1}=$

:::
::: {.column width="49%"}

a) $\displaystyle\sqrt{\sqrt{16a^2x^2}} \cdot \sqrt{a^3x} \cdot \sqrt[3]{a^{-6}x^{-3}}=$\setlength{\itemsep}{14pt}

b) $\displaystyle\sqrt{2^6y^4}\cdot\left(x^4 \cdot y^8\right)\cdot x \cdot \left(\sqrt{2^4}\right)^{-1}=$

c) $\displaystyle\left(\sqrt[3]{a^{0{,}6}} \cdot \sqrt[4]{a^{-0{,}4}}\right)^{10}=$

d) $\displaystyle\sqrt[3]{16xy^4}\sqrt[3]{4x^2y^2}\sqrt[3]{x^{-3}y^{-6}}=$
:::
::::::


```{r finish-Potenzgesetze, include=FALSE}
rm(pathToImages)
finalizePart()
```
